Measuring individual differences in the understanding of gaze cues across the lifespan

### 2022-05-20 paper/manuscript.Rmd
minor editing in intro & vali section

# Introduction 
Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences. Since children spend a large amount of their daily lives interacting with and learning from others in social contexts, many studies investigate the emergence and driving factors of social-cognitive abilities. Under social cognition, we understand the ability to explain and predict the behavior of social agents by representing and reasoning about their perspectives, knowledge, intentions, beliefs, and preferences.

Traditional tasks of social cognition (e.g., false belief change-of-location tasks) frequently build upon dichotomous outcome variables (resulting in high chance levels), small sample sizes and low numbers of trials per subject.

With these procedures, researchers could systematically track change on a group level and capture the average age at which children succeed in a given task that relies on a certain social-cognitive ability. However, poor psychometric properties may conceal relations between different aspects of cognition and also obscure developmental change.

If we want to answer questions about the co-development of social-cognitive abilities and the individual’s pace of mastering developmental milestones, we need to take variation between children seriously – both methodologically and theoretically. We argue that a systematic individual differences perspective on social-cognitive development is needed.

To study individual differences, variability in task performance needs to be reliable (i.e., systematically order individuals in the same way) and meaningful (i.e., differences in test scores correspond to differences in ability).

@@

From previous studies that tried to relate several theoretically connected constructs to each other, we see mostly failed attempts. For example, @sodian2016understanding studied the relation between several social cognition measures. Against expectation, they could not find correlations between some theoretically connected constructs (e.g. implicit false belief  and moral false belief understanding). Interestingly, nearly all measured variables were associated with their verbal IQ test. This shows that we are more likely to find associations between constructs when measures are actually designed to capture variation between individuals - similarly to how IQ tests are constructed. Therefore, it is conceivable that we are simply not able to capture existing underlying relationships with our existing tools - since they were mostly not created to quantify individual differences.

@@

To estimate the effect of inter-individual differences, we need a large sample size since since some of the effects that we are looking for might be small. Since data collection with families requires a lot of organizational effort, we want to enable data collection in-person with supervision as well as remotely without supervision. A standardized, easily accessible test procedure helps us to enable data collection at scale.

Another goal in creating new tasks should be to focus on the face value: we want to measure the underlying social-cognitive ability as straight-forward and directly as possible. Importantly, we can assess whether the task shows external validity by assessing the relationship with related constructs and factors of children's social surrounding.

In our first novel task, we concentrated on the essential ability that is involved in many social-cognitive reasoning processes: gaze cue understanding - the ability to locate and use the attentional focus of an agent. The first component is often termed gaze following - turning ones eyes in the same direction as the gaze of another agent. By acting as a 'front end ability' [@brooks2005development, p. 535], following an agent's gaze provides insights into their intentions, thoughts, and feelings. In our definition, gaze cue understanding goes one step further by including the *acting* on the gaze-cued location.

In many previous gaze following studies, the eye movement of an agent was accompanied by a congruent head movement - thus, making it hard to disentangle which information the children rely on. In our task, we control the eye movement alone to pinpoint and break down children's abilities as detailed as possible.

By implementing studies with open versus closed eyes conditions and head versus eye movement alone, researchers found that infants start gaze following in the narrow sense at the end of their first year of life (e.g., @brooks2005development). 
It is, however, unclear when and how children start to use these cues to guide their own active behavior.

@@

Adults were recruited via *Prolific*. *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool. Participants consisted of `r vali_adults$nTotal` English-speakers with an average age of `r vali_adults$meanAge` years (SD = `r vali_adults$sdAge`, range = `r vali_adults$minAge` - `r vali_adults$maxAge`, `r vali_adults$nFemales` females). 
For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour).

@@

# Validity
Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social environment [m: kurz sagen warum wir das erwarten - also dass frühere studien hier links sehen (zitieren) und die mit anderen measures of social cognition auch finden. Daher sehen wir das als indikator für validität, wenn wir das auch finden.]

@@

## Discussion
In line with previous research, We found that factors of children's social surrounding influenced their gaze cue understanding. Even though the effects are small and confidence intervals wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables [m: das ein bisschen aufdröseln - also sagen dass frühere tassk sich komplexere sahcen angeguckt haben und wir aber schon sehen, dass es schienbar systeamtische sachen gibt bei den einfachen dingen die wir hier messen].

>>>>

Maybe for abstract: Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.

# Introduction 
Social cognition – representing and reasoning about an agent’s perspectives, knowledge states, intentions, beliefs, and preferences to explain and predict their behavior – is among the best-studied phenomena in developmental research.

In recent decades, much progress has been made in determining the average age at which a specific social-cognitive ability emerges in development.

But we still know relatively little about the co-development of social-cognitive abilities, variation in the individual’s pace of mastering developmental milestones, and which factors influence a child’s proficiency.

Researchers are interested in questions concerning individual differences in the social cognition domain [@hughes2015individual]. Previous studies focused, for example, on the association of stereotypes and theory of mind [@rizzo2018theory], mental state talk and false belief understanding [@hughes2011individual], attachment quality and gaze following [@astor2020social], language and gaze following [@okumura2017individual], emotion, language, family interaction and belief understanding [@dunn1991young; @cutting1999theory; @bulgarelli2016social], and the interplay of physical and social cognition [@herrmann2010structure]. Correlational approaches have also been used to argue for and test assumptions of cognitive development theories [@mundy2007individual; @kidd2018individual; @underwood1975individual].

This is due to the fact that many developmental psychology studies track change at an (age-) group level. 
Traditional measures of social cognition are not designed to capture variation between children: 
they often rely on low trial numbers, small sample sizes, dichotomous measures, and consequently lack satisfactory psychometric properties. 
This has profound implications for what these studies can show. Poor measurement of social cognition on an individual level may conceal relations between different aspects of cognition and may obscure developmental change.

To fully understand how social-cognitive abilities emerge and relate to each other, we must take individual differences seriously.

We need tasks that capture variability in performance reliably (i.e., systematically order individuals in the same way) and meaningfully (i.e., differences in test scores correspond to differences in ability).

@@

[TODO: check Manuels references]

However, we rarely find studies addressing these issues. 
Methods, that have currently been used, are...
One of the most commonly applied measures in social cognition research is the Sally-Anne task. [TODO: fill in FB studies]
The outcome measures false belief understanding in a dichotomous way: children pass the task if they answer that the protagonist would ...
With four to five years of age, most children pass the task. From this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value. With these procedures, researchers could systematically determine the average age at which children succeed in the Sally-Anne task. However, no individual differences can be visible, especially when applying only one trial per child.

@@

To estimate the effect of inter-individual differences, we need a large sample size since some of the effects that we are looking for might be small. Since data collection with families requires a lot of organizational effort, we want to enable data collection in-person with supervision as well as remotely without supervision. A standardized, easily accessible test procedure helps us to enable data collection at scale.

Another goal in creating new tasks should be to focus on the face value: we want to measure the underlying social-cognitive ability as straight-forward and directly as possible. Importantly, we can assess whether the task shows external validity by assessing the relationship with related constructs and factors of children's social surroundings.

In our first novel task, we concentrated on the fundamental ability that is involved in many social-cognitive reasoning processes: gaze cue understanding - the ability to locate and use the attentional focus of an agent. The first component is often termed gaze following - turning ones eyes in the same direction as the gaze of another agent - and has been studied intensively [TODO: add references]. 
By acting as a 'front end ability' [@brooks2005development, p. 535], following an agent's gaze provides insights into their intentions, thoughts, and feelings. 
In our definition, gaze cue understanding goes one step further by including the *acting* on the gaze-cued location.

@@

Adults were recruited via *Prolific* [@palan2018prolific]. *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-american subject pool. Participants consisted of `r vali_adults$nTotal` English-speakers with an average age of `r vali_adults$meanAge` years (SD = `r vali_adults$sdAge`, range = `r vali_adults$minAge` - `r vali_adults$maxAge`, `r vali_adults$nFemales` females). 
For completing the study, subjects were payed above the fixed minimum wage (in average £10.00 per hour).

@@

# Validity
Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social environment. Previous studies found associations between social cognition measures and various environmental factors [@devine2018family; @hughes2004links], including family background and education [@cutting1999theory; bulgarelli2016social], number and age of siblings and family constellation [@zhang2021worse, @cassidy2005theory; @perner1994theory; @peterson2000kindred], interaction with siblings [@dunn1991young], and centre-based childcare [@bulgarelli2016social]. It is assumed that opportunities to play, communicate and argue with siblings and similarly-aged peers help children to understand the human mind. Therefore, if we find a link between gaze cue understanding and family factors, we regard this as an indicator for the predictive validity of our measure.

@@

## Discussion
We found that factors of children's social surrounding influenced their gaze cue understanding. Even though the effects are small and confidence intervals wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables. Previous studies often focused on more complex, later developing social-cognitive abilities (e.g., false belief understanding). Apparently, systematic links between family factors and social-cognitive abilities can be found even when looking at more fundamental social-cognitive abilities like gaze cue understanding.

### 2022-05-20 paper/manuscript.tex
minor editing in intro & vali section

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

@@

@@

Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences. Since children spend a large amount of their daily lives interacting with and learning from others in social contexts, many studies investigate the emergence and driving factors of social-cognitive abilities. Under social cognition, we understand the ability to explain and predict the behavior of social agents by representing and reasoning about their perspectives, knowledge, intentions, beliefs, and preferences.

Traditional tasks of social cognition (e.g., false belief change-of-location tasks) frequently build upon dichotomous outcome variables (resulting in high chance levels), small sample sizes and low numbers of trials per subject.

With these procedures, researchers could systematically track change on a group level and capture the average age at which children succeed in a given task that relies on a certain social-cognitive ability. However, poor psychometric properties may conceal relations between different aspects of cognition and also obscure developmental change.

If we want to answer questions about the co-development of social-cognitive abilities and the individual's pace of mastering developmental milestones, we need to take variation between children seriously -- both methodologically and theoretically. We argue that a systematic individual differences perspective on social-cognitive development is needed.

To study individual differences, variability in task performance needs to be reliable (i.e., systematically order individuals in the same way) and meaningful (i.e., differences in test scores correspond to differences in ability).

@@

From previous studies that tried to relate several theoretically connected constructs to each other, we see mostly failed attempts. For example, Sodian et al. (2016) studied the relation between several social cognition measures. Against expectation, they could not find correlations between some theoretically connected constructs (e.g.~implicit false belief and moral false belief understanding). Interestingly, nearly all measured variables were associated with their verbal IQ test. This shows that we are more likely to find associations between constructs when measures are actually designed to capture variation between individuals - similarly to how IQ tests are constructed. Therefore, it is conceivable that we are simply not able to capture existing underlying relationships with our existing tools - since they were mostly not created to quantify individual differences.

@@

To estimate the effect of inter-individual differences, we need a large sample size since since some of the effects that we are looking for might be small. Since data collection with families requires a lot of organizational effort, we want to enable data collection in-person with supervision as well as remotely without supervision. A standardized, easily accessible test procedure helps us to enable data collection at scale.

Another goal in creating new tasks should be to focus on the face value: we want to measure the underlying social-cognitive ability as straight-forward and directly as possible. Importantly, we can assess whether the task shows external validity by assessing the relationship with related constructs and factors of children's social surrounding.

In our first novel task, we concentrated on the essential ability that is involved in many social-cognitive reasoning processes: gaze cue understanding - the ability to locate and use the attentional focus of an agent. The first component is often termed gaze following - turning ones eyes in the same direction as the gaze of another agent. By acting as a `front end ability' (Brooks \& Meltzoff, 2005, p. 535), following an agent's gaze provides insights into their intentions, thoughts, and feelings. In our definition, gaze cue understanding goes one step further by including the \emph{acting} on the gaze-cued location.

In many previous gaze following studies, the eye movement of an agent was accompanied by a congruent head movement - thus, making it hard to disentangle which information the children rely on. In our task, we control the eye movement alone to pinpoint and break down children's abilities as detailed as possible.

By implementing studies with open versus closed eyes conditions and head versus eye movement alone, researchers found that infants start gaze following in the narrow sense at the end of their first year of life (e.g., Brooks and Meltzoff (2005)).
It is, however, unclear when and how children start to use these cues to guide their own active behavior.

@@

Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social environment {[}m: kurz sagen warum wir das erwarten - also dass frühere studien hier links sehen (zitieren) und die mit anderen measures of social cognition auch finden. Daher sehen wir das als indikator für validität, wenn wir das auch finden.{]}

@@

To estimate the effects of social surrounding on gaze cue understanding, we fit GLMMs predicting the task performance by each of our questionnaire variables, controlling for age (in months, z-transformed), data collection mode (reference category: in-person supervised) and study version (reference category: hedge version). The models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants. Therefore, our null model closely resembled the structure from our first analysis (see Analysis section of \emph{Does the balloon finding task induce variation?}; here: \texttt{performance\ \textasciitilde{}\ age\ +\ datacollection\ +\ studyversion\ +\ (symmetricPosition\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}).
In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome. For the target position, we categorized two adjacent bins as one imaginary box. To measure participants' performance, we created imaginary box boundaries around the target's landing position and examined whether the participant's click response fell into this imaginary box. Across the two study versions, we could consequently model the participant's correct response (0/1) using a \texttt{Bernoulli} distribution with a logit link function.
For model comparisons, we ran separate models, each with one of the following predictors as a fixed effects added to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subject entered childcare.
In addition, we calculated three index scores. First, we calculated a sibling variety score according to Peterson (2000). Second, we implemented the modified version of Cassidy, Fineberg, Brown, and Perkins (2005) (for more details, see Supplements). Third, based on our own data exploration, we calculated the amount of peer exposure determined as the number of siblings and the average hours spent in childcare (both z-transformed).
We compared the models using WAIC (widely applicable information criterion) scores and weights (McElreath, 2020). As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit. WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.

@@

In line with previous research, We found that factors of children's social surrounding influenced their gaze cue understanding. Even though the effects are small and confidence intervals wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables {[}m: das ein bisschen aufdröseln - also sagen dass frühere tassk sich komplexere sahcen angeguckt haben und wir aber schon sehen, dass es schienbar systeamtische sachen gibt bei den einfachen dingen die wir hier messen{]}.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-brooks2005development}{}}%
Brooks, R., \& Meltzoff, A. N. (2005). The development of gaze following and its relation to language. \emph{Developmental Science}, \emph{8}(6), 535--543. \url{https://doi.org/10.1111/j.1467-7687.2005.00445.x}

@@

@@

@@

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-sodian2016understanding}{}}%
Sodian, B., Licata, M., Kristen-Antonow, S., Paulus, M., Killen, M., \& Woodward, A. (2016). Understanding of {Goals}, {Beliefs}, and {Desires Predicts Morally Relevant Theory} of {Mind}: {A Longitudinal Investigation}. \emph{Child Development}, \emph{87}(4), 1221--1232. \url{https://doi.org/10.1111/cdev.12533}

>>>>

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

@@

Maybe for abstract: Developmental psychology is facing a dilemma: many research questions are questions about individual differences, yet, there is a lack of tasks to reliably measure these individual differences.

@@

Social cognition -- representing and reasoning about an agent's perspectives, knowledge states, intentions, beliefs, and preferences to explain and predict their behavior -- is among the best-studied phenomena in developmental research.

In recent decades, much progress has been made in determining the average age at which a specific social-cognitive ability emerges in development.

But we still know relatively little about the co-development of social-cognitive abilities, variation in the individual's pace of mastering developmental milestones, and which factors influence a child's proficiency.

Researchers are interested in questions concerning individual differences in the social cognition domain (Hughes \& Devine, 2015). Previous studies focused, for example, on the association of stereotypes and theory of mind (Rizzo \& Killen, 2018), mental state talk and false belief understanding (Hughes, Ensor, \& Marks, 2011), attachment quality and gaze following (Astor et al., 2020), language and gaze following (Okumura, Kanakogi, Kobayashi, \& Itakura, 2017), emotion, language, family interaction and belief understanding (Bulgarelli \& Molina, 2016; Cutting \& Dunn, 1999; Dunn, Brown, Slomkowski, Tesla, \& Youngblade, 1991), and the interplay of physical and social cognition (Herrmann, Hernández-Lloreda, Call, Hare, \& Tomasello, 2010). Correlational approaches have also been used to argue for and test assumptions of cognitive development theories (Kidd, Donnelly, \& Christiansen, 2018; Mundy et al., 2007 May-Jun; Underwood, 1975).

This is due to the fact that many developmental psychology studies track change at an (age-) group level.
Traditional measures of social cognition are not designed to capture variation between children:
they often rely on low trial numbers, small sample sizes, dichotomous measures, and consequently lack satisfactory psychometric properties.
This has profound implications for what these studies can show. Poor measurement of social cognition on an individual level may conceal relations between different aspects of cognition and may obscure developmental change.

To fully understand how social-cognitive abilities emerge and relate to each other, we must take individual differences seriously.

We need tasks that capture variability in performance reliably (i.e., systematically order individuals in the same way) and meaningfully (i.e., differences in test scores correspond to differences in ability).

@@

{[}TODO: check Manuels references{]}

However, we rarely find studies addressing these issues.
Methods, that have currently been used, are\ldots{}
One of the most commonly applied measures in social cognition research is the Sally-Anne task. {[}TODO: fill in FB studies{]}
The outcome measures false belief understanding in a dichotomous way: children pass the task if they answer that the protagonist would \ldots{}
With four to five years of age, most children pass the task. From this age onwards, the change-of-location task shows ceiling effects and has very limited diagnostic value. With these procedures, researchers could systematically determine the average age at which children succeed in the Sally-Anne task. However, no individual differences can be visible, especially when applying only one trial per child.

@@

To estimate the effect of inter-individual differences, we need a large sample size since some of the effects that we are looking for might be small. Since data collection with families requires a lot of organizational effort, we want to enable data collection in-person with supervision as well as remotely without supervision. A standardized, easily accessible test procedure helps us to enable data collection at scale.

Another goal in creating new tasks should be to focus on the face value: we want to measure the underlying social-cognitive ability as straight-forward and directly as possible. Importantly, we can assess whether the task shows external validity by assessing the relationship with related constructs and factors of children's social surroundings.

In our first novel task, we concentrated on the fundamental ability that is involved in many social-cognitive reasoning processes: gaze cue understanding - the ability to locate and use the attentional focus of an agent. The first component is often termed gaze following - turning ones eyes in the same direction as the gaze of another agent - and has been studied intensively {[}TODO: add references{]}.
By acting as a `front end ability' (Brooks \& Meltzoff, 2005, p. 535), following an agent's gaze provides insights into their intentions, thoughts, and feelings.
In our definition, gaze cue understanding goes one step further by including the \emph{acting} on the gaze-cued location.

@@

Our third aim was to assess whether the captured individual variation in gaze cue understanding relates to factors in children's real live social environment. Previous studies found associations between social cognition measures and various environmental factors (Devine \& Hughes, 2018), including family background and education {[}Cutting and Dunn (1999); bulgarelli2016social{]}, number and age of siblings and family constellation Cassidy, Fineberg, Brown, \& Perkins (2005), interaction with siblings (Dunn et al., 1991), and centre-based childcare (Bulgarelli \& Molina, 2016). It is assumed that opportunities to play, communicate and argue with siblings and similarly-aged peers help children to understand the human mind. Therefore, if we find a link between gaze cue understanding and family factors, we regard this as an indicator for the validity of our measure.

@@

To estimate the effects of social surrounding on gaze cue understanding, we fit GLMMs predicting the task performance by each of our questionnaire variables, controlling for age (in months, z-transformed), data collection mode (reference category: in-person supervised) and study version (reference category: hedge version). The models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants. Therefore, our null model closely resembled the structure from our first analysis (see Analysis section of \emph{Does the balloon finding task induce variation?}; here: \texttt{performance\ \textasciitilde{}\ age\ +\ datacollection\ +\ studyversion\ +\ (symmetricPosition\ \textbar{}\ subjID)\ +\ (1\ \textbar{}\ targetPosition)}).
In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome. For the target position, we categorized two adjacent bins as one imaginary box. To measure participants' performance, we created imaginary box boundaries around the target's landing position and examined whether the participant's click response fell into this imaginary box. Across the two study versions, we could consequently model the participant's correct response (0/1) using a \texttt{Bernoulli} distribution with a logit link function.
For model comparisons, we ran separate models, each with one of the following predictors as a fixed effects added to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subject entered childcare.
In addition, we calculated three index scores. First, we calculated a sibling variety score according to Peterson (2000). Second, we implemented the modified version of Cassidy et al. (2005) (for more details, see Supplements). Third, based on our own data exploration, we calculated the amount of peer exposure determined as the number of siblings and the average hours spent in childcare (both z-transformed).
We compared the models using WAIC (widely applicable information criterion) scores and weights (McElreath, 2020). As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit. WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.

@@

We found that factors of children's social surrounding influenced their gaze cue understanding. Even though the effects are small and confidence intervals wide, it is remarkable that we were able to detect relationships between this fundamental social-cognitive ability and very distant, real life variables. Previous studies often focused on more complex, later developing social-cognitive abilities (e.g., false belief understanding). Apparently, systematic links between family factors and social-cognitive abilities can be found even when looking at more fundamental social-cognitive abilities like gaze cue understanding.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-astor2020social}{}}%
Astor, K., Lindskog, M., Forssman, L., Kenward, B., Fransson, M., Skalkidou, A., \ldots{} Gredebäck, G. (2020). Social and emotional contexts predict the development of gaze following in early infancy. \emph{Royal Society Open Science}, \emph{7}(9), 201178. \url{https://doi.org/10.1098/rsos.201178}

\leavevmode\vadjust pre{\hypertarget{ref-brooks2005development}{}}%
Brooks, R., \& Meltzoff, A. N. (2005). The development of gaze following and its relation to language. \emph{Developmental Science}, \emph{8}(6), 535--543. \url{https://doi.org/10.1111/j.1467-7687.2005.00445.x}

\leavevmode\vadjust pre{\hypertarget{ref-bulgarelli2016social}{}}%
Bulgarelli, D., \& Molina, P. (2016). Social {Cognition} in {Preschoolers}: {Effects} of {Early Experience} and {Individual Differences}. \emph{Frontiers in Psychology}, \emph{7}. \url{https://doi.org/10.3389/fpsyg.2016.01762}

@@

\leavevmode\vadjust pre{\hypertarget{ref-cutting1999theory}{}}%
Cutting, A. L., \& Dunn, J. (1999). Theory of {Mind}, {Emotion Understanding}, {Language}, and {Family Background}: {Individual Differences} and {Interrelations}. \emph{Child Development}, \emph{70}(4), 853--865. \url{https://doi.org/10.1111/1467-8624.00061}

\leavevmode\vadjust pre{\hypertarget{ref-devine2018family}{}}%
Devine, R. T., \& Hughes, C. (2018). Family {Correlates} of {False Belief Understanding} in {Early Childhood}: {A Meta-Analysis}. \emph{Child Development}, \emph{89}(3), 971--987. \url{https://doi.org/10.1111/cdev.12682}

\leavevmode\vadjust pre{\hypertarget{ref-dunn1991young}{}}%
Dunn, J., Brown, J., Slomkowski, C., Tesla, C., \& Youngblade, L. (1991). \href{https://www.ncbi.nlm.nih.gov/pubmed/1786720}{Young children's understanding of other people's feelings and beliefs: Individual differences and their antecedents}. \emph{Child Development}, \emph{62}(6), 1352--1366.

@@

\leavevmode\vadjust pre{\hypertarget{ref-herrmann2010structure}{}}%
Herrmann, E., Hernández-Lloreda, M. V., Call, J., Hare, B., \& Tomasello, M. (2010). The {Structure} of {Individual Differences} in the {Cognitive Abilities} of {Children} and {Chimpanzees}. \emph{Psychological Science}, \emph{21}(1), 102--110. \url{https://doi.org/10.1177/0956797609356511}

\leavevmode\vadjust pre{\hypertarget{ref-hughes2015individual}{}}%
Hughes, C., \& Devine, R. T. (2015). Individual {Differences} in {Theory} of {Mind From Preschool} to {Adolescence}: {Achievements} and {Directions}. \emph{Child Development Perspectives}, \emph{9}(3), 149--153. \url{https://doi.org/10.1111/cdep.12124}

\leavevmode\vadjust pre{\hypertarget{ref-hughes2011individual}{}}%
Hughes, C., Ensor, R., \& Marks, A. (2011). Individual differences in false belief understanding are stable from 3 to 6 years of age and predict children's mental state talk with school friends. \emph{Journal of Experimental Child Psychology}, \emph{108}(1), 96--112. \url{https://doi.org/10.1016/j.jecp.2010.07.012}

\leavevmode\vadjust pre{\hypertarget{ref-kidd2018individual}{}}%
Kidd, E., Donnelly, S., \& Christiansen, M. H. (2018). Individual {Differences} in {Language Acquisition} and {Processing}. \emph{Trends in Cognitive Sciences}, \emph{22}(2), 154--169. \url{https://doi.org/10.1016/j.tics.2017.11.006}

@@

\leavevmode\vadjust pre{\hypertarget{ref-mundy2007individual}{}}%
Mundy, P., Block, J., Delgado, C., Pomares, Y., Van Hecke, A. V., \& Parlade, M. V. (2007 May-Jun). Individual differences and the development of joint attention in infancy. \emph{Child Development}, \emph{78}(3), 938--954. \url{https://doi.org/10.1111/j.1467-8624.2007.01042.x}

\leavevmode\vadjust pre{\hypertarget{ref-okumura2017individual}{}}%
Okumura, Y., Kanakogi, Y., Kobayashi, T., \& Itakura, S. (2017). Individual differences in object-processing explain the relationship between early gaze-following and later language development. \emph{Cognition}, \emph{166}, 418--424. \url{https://doi.org/10.1016/j.cognition.2017.06.005}

\leavevmode\vadjust pre{\hypertarget{ref-perner1994theory}{}}%
Perner, J., Ruffman, T., \& Leekam, S. R. (1994). Theory of {Mind Is Contagious}: {You Catch It} from {Your Sibs}. \emph{Child Development}, \emph{65}(4), 1228--1238. \url{https://doi.org/10.2307/1131316}

@@

\leavevmode\vadjust pre{\hypertarget{ref-rizzo2018theory}{}}%
Rizzo, M. T., \& Killen, M. (2018). Theory of mind is related to children's resource allocations in gender stereotypic contexts. \emph{Developmental Psychology}, \emph{54}(3), 510. \url{https://doi.org/10.1037/dev0000439}

@@

\leavevmode\vadjust pre{\hypertarget{ref-underwood1975individual}{}}%
Underwood, B. J. (1975). Individual differences as a crucible in theory construction. \emph{American Psychologist}, \emph{30}(2), 128--134. \url{https://doi.org/10.1037/h0076759}

\leavevmode\vadjust pre{\hypertarget{ref-zhang2021worse}{}}%
Zhang, Z., Yu, H., Long, M., \& Li, H. (2021). Worse {Theory} of {Mind} in {Only-Children Compared} to {Children With Siblings} and {Its Intervention}. \emph{Frontiers in Psychology}, \emph{12}, 5073. \url{https://doi.org/10.3389/fpsyg.2021.754168}
